---
title: "Homework 6 Extra"
author: "Lina Sinsheimer"
format: html
embed-resources: true
editor: visual
---

```{r}
#| message: false
library(tidyverse)
library(moderndive)
library(broom)
library(ggplot2)
theme_set(theme_minimal())
```

```{r}
data(bikes, package = "bayesrules")
glimpse(bikes)
```

## Question 0

How many rows are in the dataset? 500

What does each row represent? Each row represents a day of the year, and gives information about what it was like on each day.

What dates does the dataset cover? 1/1/2011 - 12/31/2012

What is the highest observed ridership in the dataset? 6946

What was the highest wind speed recorded in the dataset? 34.00002

## Question 1

```{r}
cor(bikes$rides, bikes$temp_feel)

```

```{r}
cor(bikes$rides, bikes$windspeed)
```

## Question 2

```{r}
bikes$wind_kph <- bikes$windspeed * 1.61
```

```{r}
cor(bikes$windspeed, bikes$wind_kph)
```

This has a correlation of 1 because it is completely linear. For every 1MPH increase, there is a 1.61 KPH increase. There is no variability to this, therefore the correlation is 1.

## Question 3

```{r}
wind_mph <- lm(rides ~ windspeed, data = bikes)
broom::tidy(wind_mph)

```

```{r}
wind_kphlm <- lm(rides ~ wind_kph, data = bikes)
broom::tidy(wind_kphlm)
```

The intercepts are the same because the intercept represents the predicted amount of rides when the wind speed is zero. The coefficients are different because every mile is 1.61 kilometers, and thus the coefficients are different to account for the different units of measurements.

## Question 4

For mph: 4205 + -55.52 \* 20 = 3094.6 . This is the intercept + the slope \* wind speed.

For kph: 4205 + -34.49 \* 20 = 3515.2 .

## Question 5

```{r}
bikes$tempc <- (bikes$temp_feel - 32) * 5/9
```

```{r}
multipletemps <- lm(rides ~ wind_kph + tempc, data = bikes)
tidy(multipletemps)
```

For a one kilometer increase in wind speed, the model expects a decrease of 19.84 in the number of rides.

For a one degree Celsius increase in temperature, the model expects an increase of 143.23 in the number of rides.

When the wind speed is 0 and the temperature is 0, the model expects 942 rides.

## Question 6

```{r}
pred_df <- tibble(
  situation = 1:3,
  tempc = c(25, 15, 10),
  wind_kph = c(15, 5, 40)
)

pred_df

predict(multipletemps, pred_df)
```

1: 4225.647

2: 2991.728

3: 1581.078

## Question 7

```{r}
weekends <- lm(rides ~ wind_kph + tempc + weekend, data = bikes)
tidy(weekends)
```

When it is the weekend, the rides decrease by 713.

## Question 8

```{r}
mean(bikes$wind_kph)
mean(bikes$temp_actual)
```

```{r}
df1 <- tibble(
  situation = 1,
  tempc = c(63.3),
  wind_kph = c(20.96),
  weekend = TRUE
)

predict(weekends, df1)
```

For weekends, after taking the average temperature and windspeed, the predicted number of riders would be 8957.

```{r}
df2 <- tibble(
  situation = 1,
  tempc = c(63.3),
  wind_kph = c(20.96),
  weekend = FALSE
)

predict(weekends, df2)
```

For week days, after taking the average windspeed and temperature, the predicted number of rides would be 9670.

## Question 9

```{r}
bikerides <- predict(weekends)
residuals <- bikes$rides - bikerides
```

The day where the model was most wrong was 10/29/2012. This is the day that Hurricane Sandy landed on the US East Coast, which resulted in only 20 bike rides.
