---
title: "Homework 7"
author: Lina Sinsheimer
embed-resources: true
format: html
editor: visual
---

## Question 1

```{r}
#| message: false
library(tidyverse)
library(here)
library(moderndive)
library(dplyr)
library(ggplot2)
theme_set(theme_minimal())

nobel_winners <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/nobel_winners.csv")
```

```{r}
nobel_winners_flt <- nobel_winners %>% 
  filter(category != "Peace") %>% 
  mutate(is_us = if_else(birth_country == "United States of America", 1, 0))
```

```{r}
true_prop <- nobel_winners_flt %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))

ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  labs(x = "Proportion")
```

```{r}
set.seed(33)
# Random sample 
our_sample <- sample_n(nobel_winners_flt, 
                       size = 25, 
                       replace = F)

sample_prop <- our_sample %>% 
  group_by(is_us) %>% 
  summarise(prop = n()/nrow(our_sample))

# How does our proportion look like? 
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_prop[2,2][[1]], linetype = "dashed")  + 
  geom_vline(xintercept = sample_prop[2,2][[1]], linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

-   In this scenario, what is the population? The people who have won scientific Nobel Prize.

-   What is the sampling frame? The 25 person sample that comes from the population.

-   What does the black line represent? The actual proportion of Nobel Prize winners who were born in the USA within the population.

-   What does the red line represent? The sampled proportion of Nobel Prize winners, but just in the proportion.

## Question 2

```{r}
sample2 <- nobel_winners_flt %>%
  rep_sample_n(size=25, reps=50)
sample_prop1 <- sample2 %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(is_us)/25)
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = mean(nobel_winners_flt$is_us), linetype = "dashed")  + 
  geom_vline(xintercept = mean(sample_prop1$prop), linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

## Question 3

```{r}
sample3 <- nobel_winners_flt %>%
  rep_sample_n (size=100, reps=50)
sample_prop2 <- sample3 %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(is_us)/100)
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = mean(nobel_winners_flt$is_us), linetype = "dashed")  + 
  geom_vline(xintercept = mean(sample_prop2$prop), linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

The sample with the bigger sample has less variance, because when you have more data points, you are able to have a more accurate estimate.

## Question 4

```{r}
sd_sample_25 <- sd(sample_prop1$prop)

sd_sample_100 <- sd(sample_prop2$prop)

sd_sample_25
sd_sample_100

```

These results do support my argument that a bigger sample has less variance. The standard deviation being smaller for the 100 size samples indicates that there is less variability in our estimates as the sample size increases.

## Question 5

```{r}
nwfltgender <- nobel_winners_flt %>%
   mutate(is_f = if_else(gender == "Female", 1, 0))
sample5 <- nwfltgender %>%
  rep_sample_n(size=100, reps=50)
sample_prop5 <- sample5 %>% 
  group_by(replicate) %>% 
  summarise(prop = sum(is_f)/100)
true_propg <- nwfltgender %>% 
  group_by(is_f) %>% 
  summarise(prop = n()/nrow(nobel_winners_flt))
ggplot() + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,1)) + 
  geom_vline(xintercept = true_propg[2,2][[1]], linetype = "dashed")  + 
  geom_vline(xintercept = sample_prop5[2,2][[1]], linetype = "dotted", col = "red") +
  labs(x = "Proportion")
```

## Question 6

The Central Limit Thereom states that the more samples that you take from a population, the more normal the distribution will become, and the samples will become closer to the mean, making it more narrow (less variance). This thereom allows for us to make statistical inferences about a population, as you can never know the true proportion of all of the population (you can't just get all of the population).
