---
title: "project-idea"
author: "Lina Sinsheimer"
format: html
editor: visual
embed-resources: true
---

```{r}
library(tidyverse)
library(dplyr)
library(readxl)
wwcteam <- read_excel("Downloads/SOC229 WWC.xlsx")
wwcplayer <- read_excel("Downloads/Untitled spreadsheet-2xlsx")
```

```{r}
glimpse(wwcteam)
```

```{r}
glimpse(wwcplayer)
```

For my final project, I would like to look at the 2023 Women's World Cup data. I have scraped both the team data and player data from fbref. There are many things that I could do with this data, but the vast amount of information this table gives me lots of options. Some research questions that I have are:

-   How does age predict win percentage in WWC?

-   How does age predict the number of goals scored?

-   Do the players who play in European clubs end up being more successful than those who play in the NWSL?

I have also considered creating a scouting report for teams - I think this would be the most applicable thing that I could do for my job.

Ethan: He is thinking about creating a predictive model of current MLB players and how likely they are to make the hall in fame

Aiyanna: She is thinking about how to think about whether the Knicks are actually good or not. She is not 100% sure on how exactly she is going to do that, but that is her general thought process.
